Toxic Code Snippets on Stack Overflow

### 2018-11-24 cloverflow-tse/cloverflow.tex
Updated the authors' affiliations in the response letter and completed the cross-check that all the changes in the response letter have been applied to the paper. Start proofreading the paper.
Finished checking the added parts in the paper (with other minor fixes)

We applied different mechanisms to ensure the validity of the clone pairs we
classified.  First, we used two widely-used clone detection tools, Simian and
SourcererCC.  We tried five other clone detectors but could not add them to the
study due to their scalability issues and susceptibility to incomplete code
snippets. We adopted Bellon's agreement metric~\cite{Bellon2007} to merge clone
pairs for the manual classification and avoid double counting of the same clone
pairs. We studied the impact of choosing different thresholds for Bellon's clone agreement and the minimum clone
size of the two clone detectors and selected the optimal values.
Nevertheless, our study might still suffer from false negatives,
i.e.,~online code clones that are not reported by the tools or are filtered out
by the size (less than 10 lines) within the clone detection process. We selected
accepted answers on Stack Overflow in this study to focus on code snippets that
solve the question's problem and are often shown on top of the answer list.
We investigated the 72,365 Stack Overflow code snippets used in our study and
found that 62,245 of them (86\%) are also the highest voted answers.
We plan to incorporate the highest voted answers in future work.
We analysed the Stack Overflow data snapshot of January 2016. 
The findings may be different based on the newer snapshots. 
However, we do not expect large differences of the findings 
if we update the data set. The reason is that the Stack Overflow answers 
are rarely modified. Moreover, updating the dataset would eliminate the 
possibility to study the evolution of outdated answers.

@@

The detailed investigation of the 100 outdated answers on Stack Overflow may not
fully capture what Stack Overflow visitors actually do when they already expect
an outdated answer. However, our investigation tries to at least shade light on
this by comparing the popularity of the outdated answer and the newer answers
based on the number of votes. This may be affected by the duration that the
answers appear on a Stack Overflow post. The newer answers have less visibility
compared to the older answers.

@@

Regarding the few number of toxic code snippets in Stack Overflow posts and code reuse in
GitHub, this is partially due to the data set of (only) 111 Java projects from
the Qualitas corpus. The clones (and the discovered outdated code and
potentially license-violating code snippets) reported in this paper are only
subject to these 111 projects. The number may increase if we expand the amount
of open source projects. Moreover, this study only focuses on Java, and the
situation may be worse or better for other programming languages.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. He was supervised by Dr.~Jens Krinke and Dr.~David Clark. His research interests include code search, code clone detection, software plagiarism, search-based software engineering, and mining software repository.
\end{IEEEbiography}
\vspace{-1cm}

>>>>

We applied different mechanisms to ensure the validity of the clone pairs we
classified.  First, we used two widely-used clone detection tools, Simian and
SourcererCC.  We tried five other clone detectors but could not add them to the
study due to their scalability issues and susceptibility to incomplete code
snippets. We adopted Bellon's agreement metric~\cite{Bellon2007} to merge clone
pairs for the manual classification and avoid double counting of the same clone
pairs. We studied the impact of choosing different thresholds for Bellon's clone agreement and the minimum clone
size of the two clone detectors and selected the optimal values.
Nevertheless, our study might still suffer from false negatives,
i.e.,~online code clones that are not reported by the tools or are filtered out
by the size (less than 10 lines) within the clone detection process. We selected
accepted answers on Stack Overflow in this study to focus on code snippets that
solve the question's problem and are often shown on top of the answer list.
We investigated the 72,365 Stack Overflow code snippets used in our study and
found that 62,245 of them (86\%) are also the highest voted answers.
We plan to incorporate the highest voted answers in future work.
We analysed the Stack Overflow data snapshot of January 2016. 
The findings may differ from using the newer snapshots. 
However, we do not expect large differences of the findings 
if we update the data set. The reason is that the Stack Overflow answers 
are rarely modified. Moreover, updating the dataset would eliminate the 
possibility to study the evolution of outdated answers.

@@

The detailed investigation of the 100 outdated answers on Stack Overflow may not
fully capture what Stack Overflow visitors actually do when they already expect
an outdated answer. Our investigation tries to at least shade light on
this by comparing the popularity of the outdated answer and the newer answers
based on the number of votes. Nonetheless, this may be affected by the duration that the
answers appear on a Stack Overflow post. The newer answers have less visibility
compared to the older answers.

@@

Regarding the few number of toxic code snippets in Stack Overflow posts and code reuse in
GitHub, this is partially due to the data set of (only) 111 Java projects from
the Qualitas corpus. The clones and the discovered outdated code and
potentially license-violating code snippets reported in this paper are only
subject to these 111 projects. The number may increase if we expand the amount
of open source projects. Moreover, this study only focuses on Java, and the
situation may be worse or better for other programming languages.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. He was supervised by Dr.~Jens Krinke and Dr.~David Clark. His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repository. More info at \url{http://mucc.mahidol.ac.th/~chaiyong.rag/}.
\end{IEEEbiography}
\vspace{-1cm}

### 2018-11-24 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Finished checking the added parts in the paper (with other minor fixes)

% 2. Complete the paper data
\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$\footnote{This work has been done while the first and the third author were PhD students at CREST, University College London},~Jens Krinke$^\dagger$,~Matheus Paixao$^\ddagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
\newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
\newcommand{\myEmail}{chaiyong.rag@mahidol.ac.th, j.krinke@ucl.ac.uk, matheus.paixao@uece.br, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
%\newcommand{\mySecEmail}{}
\newcommand{\myTitle}{Cover Letter for the Reviewers of the Paper \\ ``Toxic Code Snippets on Stack Overflow''}
\newcommand{\myShortTitle}{Cover Letter}
\newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
\newcommand{\myDept}{Mahidol University (Thailand)$^\ast$, University College London (UK)$^\dagger$, 
	State University of Ceara (Brazil)$^\ddagger$,
	University of Molise (Italy)$^\star$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s). The five other intents represent other cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and were fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer.

>>>>

% 2. Complete the paper data
\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$\footnote{This work has been done while the first and the third author were PhD students at CREST, University College London, UK},~Jens Krinke$^\dagger$,~Matheus Paixao$^\ddagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
\newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
\newcommand{\myEmail}{chaiyong.rag@mahidol.ac.th, j.krinke@ucl.ac.uk, matheus.paixao@uece.br, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
%\newcommand{\mySecEmail}{}
\newcommand{\myTitle}{Cover Letter for the Reviewers of the Paper \\ ``Toxic Code Snippets on Stack Overflow''}
\newcommand{\myShortTitle}{Cover Letter}
\newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
\newcommand{\myDept}{Mahidol University (Thailand)$^\ast$, University College London (UK)$^\dagger$, 
	State University of Ceara (Brazil)$^\ddagger$,
	University of Molise (Italy)$^\star$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part. The five other intents represent other cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and were fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer.
